Check Coverage

### 2019-08-07 analysis/merge_data.Rmd
Standardize trait column names, simplify trait matrix column selection.

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  #bind_rows() %>%
  filter(study_id %in% coverage$study_id)
```

>>>>

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  filter(study_id %in% coverage$study_id)
```

```{r}
usethis::use_data(biotime_traits)
```

Get FD metrics for each study 
```{r}
load(here::here("data", "biotime_traits.rda"))

get_fd <- function(data){
  #print(max(data$record_id))
  species_mat <- data %>%
    select(year, id) %>% 
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

  years <- data %>% 
    select(year) %>%
    distinct() %>%
    arrange(year)

  trait_mat <- data %>%
    select(-c(id, taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, sourceName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
    mutate_at(vars(-id), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
    arrange(id) %>%
    column_to_rownames("id")

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .)
}

get_fd_safe <- possibly(get_fd, NA)

test_data <- biotime_traits %>% 
  group_by(study_id, plot) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  filter(!is.na(metrics)) %>%
  select(-data) %>%
  unnest()
```
